---
title: "R Programming Hw4"
author: "Amy Fox"
date: "October 24, 2018"
output: 
  pdf_document:
        keep_tex: true
---

```{r}
knitr::opts_chunk$set(message = FALSE)
```

Load necessary packages
```{r}
library(readr)
library(tidyr)
library(dplyr)
library(forcats)
library(broom)
library(purrr)
library(ggplot2)
library(knitr)

```

Read in homicide csv

```{r}
homicides <- read_csv("../data/homicide-data.csv")
```

See first few lines of data to see what's there
```{r}
head(homicides)
```

Unite the city and state columns to make a general location column   
Remove Tulsa, AL because does not exist and skews data
```{r}

homicides <- homicides %>%
  unite(col = "location", c("city", "state"),
        sep = ", ") %>%
  filter(location !="Tulsa, AL")

```

*Key for myself*  
*unsolved = closed without arrest or open/no arrest*

Create new dataframe with unsolved cases info  
Select only necessary columns  
Make a new True/False column for unsolved cases  
Group by the location and summarize the number of unsolved and the total cases  

```{r}
unsolved_df <- homicides %>%
  select(location, disposition) %>%
  mutate(unsolved = disposition != "Closed by arrest") %>%
  group_by(location) %>%
  summarise(total_cases = n(), unsolved = sum(unsolved))

head(unsolved_df)

```

Create new dataframe with only data for Baltimore  
Perform proportion test on Baltimore cases  
Tidy prop_test data 

```{r}
Baltimore_df <- unsolved_df %>%
  filter(location == "Baltimore, MD")

Baltimore_prop_test <- prop.test(x= Baltimore_df$unsolved, 
                                  n = Baltimore_df$total_cases)

#print output of prop.test
Baltimore_prop_test

# print tidied prop.test
tidied_Baltimore_prop_test <- tidy(Baltimore_prop_test)
tidied_Baltimore_prop_test

#pull out estimate proportion and confidence intervals
tidied_Baltimore_prop_test$estimate
tidied_Baltimore_prop_test$conf.low
tidied_Baltimore_prop_test$conf.high
```

Create new column with prop.test of each city using map2  
Create new column with tidied proptest data  
Unnest data --> tidy data from list to df  
Reorder location by estimate  
  
Plot cities according to the estimate for unsolved cases showing the 95% confidence interval  
Change x axis from decimal to percent  
Add labels  

(Must change fig.width to fig_width for PDF)

```{r fig.width = 4, fig.height = 9}

tidy_cities_prop <- unsolved_df %>%
  mutate(my_prop_test = map2(unsolved, total_cases, prop.test),
         tidy_prop_test = map(my_prop_test, tidy)) %>%
  unnest(tidy_prop_test, .drop = TRUE) %>%
  mutate(location = factor(location, levels = location[order(estimate)]))
  

tidy_cities_prop %>%
ggplot(aes(estimate, location)) +
  geom_point(color = "white") +
  geom_errorbarh(aes(xmin = conf.low, 
                     xmax = conf.high, 
                     height = 0),  color = "white") +
  scale_x_continuous(labels= scales::percent) +
  ggtitle("Unsolved homicides by city", subtitle = "Bars show 95% confidence interval") +
  xlab("Percent of homicdes that are unsolved")+
  ylab("") +
  theme_dark()

```

